\huge Risk of non-Hodgkin lymphoma under hypothetical interventions with guaranteed positivity

### 2023-06-30 reports/SER (2023)/resources/intervention-density.tex
update paper

% Created by tikzDevice version 0.12.3.1 on 2023-06-08 17:09:01
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,195.13);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (271.01,195.13);
\end{scope}
\begin{scope}
\path[clip] ( 36.40, 72.85) rectangle (265.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 36.40, 72.85) rectangle (265.01,195.13);
\definecolor{fillColor}{RGB}{163,207,235}

\path[fill=fillColor] ( 46.79, 78.40) rectangle ( 58.33, 78.43);

\path[fill=fillColor] ( 58.33, 78.40) rectangle ( 69.88, 78.79);

\path[fill=fillColor] ( 69.88, 78.40) rectangle ( 81.43, 78.79);

\path[fill=fillColor] ( 81.43, 78.40) rectangle ( 92.97, 79.38);

\path[fill=fillColor] ( 92.97, 78.40) rectangle (104.52, 79.86);

\path[fill=fillColor] (104.52, 78.40) rectangle (116.06, 80.51);

\path[fill=fillColor] (116.06, 78.40) rectangle (127.61, 83.35);

\path[fill=fillColor] (127.61, 78.40) rectangle (139.16, 85.54);

\path[fill=fillColor] (139.16, 78.40) rectangle (150.70,103.29);

\path[fill=fillColor] (150.70, 78.40) rectangle (162.25,102.34);

\path[fill=fillColor] (162.25, 78.40) rectangle (173.80,189.57);

\path[fill=fillColor] (173.80, 78.40) rectangle (185.34,123.53);

\path[fill=fillColor] (185.34, 78.40) rectangle (196.89,106.28);

\path[fill=fillColor] (196.89, 78.40) rectangle (208.44, 88.77);

\path[fill=fillColor] (208.44, 78.40) rectangle (219.98, 85.04);

\path[fill=fillColor] (219.98, 78.40) rectangle (231.53, 78.97);

\path[fill=fillColor] (231.53, 78.40) rectangle (243.07, 79.17);

\path[fill=fillColor] (243.07, 78.40) rectangle (254.62, 78.43);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 3.2pt] ( 46.79, 78.40) rectangle ( 58.33, 78.43);

\path[draw=drawColor,line width= 3.2pt] ( 58.33, 78.40) rectangle ( 69.88, 78.73);

\path[draw=drawColor,line width= 3.2pt] ( 69.88, 78.40) rectangle ( 81.43, 78.76);

\path[draw=drawColor,line width= 3.2pt] ( 81.43, 78.40) rectangle ( 92.97, 79.20);

\path[draw=drawColor,line width= 3.2pt] ( 92.97, 78.40) rectangle (104.52, 79.47);

\path[draw=drawColor,line width= 3.2pt] (104.52, 78.40) rectangle (116.06, 79.85);

\path[draw=drawColor,line width= 3.2pt] (116.06, 78.40) rectangle (127.61, 82.26);

\path[draw=drawColor,line width= 3.2pt] (127.61, 78.40) rectangle (139.16, 83.65);

\path[draw=drawColor,line width= 3.2pt] (139.16, 78.40) rectangle (150.70, 93.74);

\path[draw=drawColor,line width= 3.2pt] (150.70, 78.40) rectangle (162.25, 93.20);

\path[draw=drawColor,line width= 3.2pt] (162.25, 78.40) rectangle (173.80,122.26);

\path[draw=drawColor,line width= 3.2pt] (173.80, 78.40) rectangle (185.34,132.11);

\path[draw=drawColor,line width= 3.2pt] (185.34, 78.40) rectangle (196.89,142.20);

\path[draw=drawColor,line width= 3.2pt] (196.89, 78.40) rectangle (208.44,112.28);

\path[draw=drawColor,line width= 3.2pt] (208.44, 78.40) rectangle (219.98,101.97);

\path[draw=drawColor,line width= 3.2pt] (219.98, 78.40) rectangle (231.53, 82.12);

\path[draw=drawColor,line width= 3.2pt] (231.53, 78.40) rectangle (243.07, 81.28);

\path[draw=drawColor,line width= 3.2pt] (243.07, 78.40) rectangle (254.62, 78.54);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (174.29, 72.85) -- (174.29,195.13);

\path[draw=drawColor,line width= 3.2pt,line join=round,line cap=round] ( 36.40, 72.85) rectangle (265.01,195.13);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45, 75.31) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,102.18) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,129.06) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,155.94) {0.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 31.45,182.82) {0.8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65, 78.40) --
	( 36.40, 78.40);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,105.28) --
	( 36.40,105.28);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,132.16) --
	( 36.40,132.16);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,159.04) --
	( 36.40,159.04);

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 33.65,185.92) --
	( 36.40,185.92);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 3.2pt,line join=round] ( 46.79, 70.10) --
	( 46.79, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (137.13, 70.10) --
	(137.13, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (206.31, 70.10) --
	(206.31, 72.85);

\path[draw=drawColor,line width= 3.2pt,line join=round] (259.48, 70.10) --
	(259.48, 72.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 46.79, 61.70) {0.001};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (137.13, 61.70) {0.05};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (206.31, 61.70) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (259.48, 61.70) {10};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (150.70, 47.75) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 12.20,133.99) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 43.99, 23.00) rectangle (257.42, 35.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 43.99, 30.90) {Distribution:\ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (105.42, 28.00) rectangle (117.42, 40.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{163,207,235}
\definecolor{fillColor}{RGB}{163,207,235}

\path[draw=drawColor,line width= 1.2pt,fill=fillColor] (106.92, 29.50) rectangle (115.92, 38.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (203.85, 28.00) rectangle (215.85, 40.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 1.2pt] (205.35, 29.50) rectangle (214.35, 38.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (122.42, 30.90) {Post-intervention\ \ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (220.85, 30.90) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 72.41,  0.00) rectangle (229.00, 12.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 72.41,  7.90) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (164.74,  5.00) rectangle (176.74, 17.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (170.74,  5.00) -- (170.74, 17.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.90] at (181.74,  7.90) {0.25 mg/m\textsuperscript{3}};
\end{scope}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2023-06-28 16:02:21
% !TEX encoding = UTF-8 Unicode
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (271.01,195.13);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (271.01,195.13);
\end{scope}
\begin{scope}
\path[clip] ( 34.23, 80.08) rectangle (265.01,189.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 34.23, 80.08) rectangle (265.01,189.13);
\definecolor{fillColor}{RGB}{163,207,235}

\path[fill=fillColor] ( 44.72, 85.04) rectangle ( 56.38, 85.06);

\path[fill=fillColor] ( 56.38, 85.04) rectangle ( 68.04, 85.38);

\path[fill=fillColor] ( 68.04, 85.04) rectangle ( 79.69, 85.38);

\path[fill=fillColor] ( 79.69, 85.04) rectangle ( 91.35, 85.91);

\path[fill=fillColor] ( 91.35, 85.04) rectangle (103.00, 86.33);

\path[fill=fillColor] (103.00, 85.04) rectangle (114.66, 86.91);

\path[fill=fillColor] (114.66, 85.04) rectangle (126.31, 89.45);

\path[fill=fillColor] (126.31, 85.04) rectangle (137.97, 91.40);

\path[fill=fillColor] (137.97, 85.04) rectangle (149.62,107.23);

\path[fill=fillColor] (149.62, 85.04) rectangle (161.28,106.39);

\path[fill=fillColor] (161.28, 85.04) rectangle (172.93,184.17);

\path[fill=fillColor] (172.93, 85.04) rectangle (184.59,125.28);

\path[fill=fillColor] (184.59, 85.04) rectangle (196.25,109.90);

\path[fill=fillColor] (196.25, 85.04) rectangle (207.90, 94.28);

\path[fill=fillColor] (207.90, 85.04) rectangle (219.56, 90.96);

\path[fill=fillColor] (219.56, 85.04) rectangle (231.21, 85.54);

\path[fill=fillColor] (231.21, 85.04) rectangle (242.87, 85.72);

\path[fill=fillColor] (242.87, 85.04) rectangle (254.52, 85.06);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 3.2pt] ( 44.72, 85.04) rectangle ( 56.38, 85.06);

\path[draw=drawColor,line width= 3.2pt] ( 56.38, 85.04) rectangle ( 68.04, 85.33);

\path[draw=drawColor,line width= 3.2pt] ( 68.04, 85.04) rectangle ( 79.69, 85.35);

\path[draw=drawColor,line width= 3.2pt] ( 79.69, 85.04) rectangle ( 91.35, 85.74);

\path[draw=drawColor,line width= 3.2pt] ( 91.35, 85.04) rectangle (103.00, 85.99);

\path[draw=drawColor,line width= 3.2pt] (103.00, 85.04) rectangle (114.66, 86.33);

\path[draw=drawColor,line width= 3.2pt] (114.66, 85.04) rectangle (126.31, 88.47);

\path[draw=drawColor,line width= 3.2pt] (126.31, 85.04) rectangle (137.97, 89.72);

\path[draw=drawColor,line width= 3.2pt] (137.97, 85.04) rectangle (149.62, 98.72);

\path[draw=drawColor,line width= 3.2pt] (149.62, 85.04) rectangle (161.28, 98.23);

\path[draw=drawColor,line width= 3.2pt] (161.28, 85.04) rectangle (172.93,124.15);

\path[draw=drawColor,line width= 3.2pt] (172.93, 85.04) rectangle (184.59,132.93);

\path[draw=drawColor,line width= 3.2pt] (184.59, 85.04) rectangle (196.25,141.93);

\path[draw=drawColor,line width= 3.2pt] (196.25, 85.04) rectangle (207.90,115.25);

\path[draw=drawColor,line width= 3.2pt] (207.90, 85.04) rectangle (219.56,106.06);

\path[draw=drawColor,line width= 3.2pt] (219.56, 85.04) rectangle (231.21, 88.35);

\path[draw=drawColor,line width= 3.2pt] (231.21, 85.04) rectangle (242.87, 87.60);

\path[draw=drawColor,line width= 3.2pt] (242.87, 85.04) rectangle (254.52, 85.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (173.43, 80.08) -- (173.43,189.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 34.23, 80.08) rectangle (265.01,189.13);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28, 82.28) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,106.25) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,130.22) {0.4};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,154.19) {0.6};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 29.28,178.16) {0.8};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48, 85.04) --
	( 34.23, 85.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,109.01) --
	( 34.23,109.01);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,132.98) --
	( 34.23,132.98);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,156.95) --
	( 34.23,156.95);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 31.48,180.92) --
	( 34.23,180.92);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 44.72, 77.33) --
	( 44.72, 80.08);

\path[draw=drawColor,line width= 0.4pt,line join=round] (135.92, 77.33) --
	(135.92, 80.08);

\path[draw=drawColor,line width= 0.4pt,line join=round] (205.75, 77.33) --
	(205.75, 80.08);

\path[draw=drawColor,line width= 0.4pt,line join=round] (259.43, 77.33) --
	(259.43, 80.08);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 44.72, 69.62) {0.001};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (135.92, 69.62) {0.05};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (205.75, 69.62) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (259.43, 69.62) {10};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (149.62, 56.56) {Exposure to soluble MWF (mg/m\textsuperscript{3})};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 11.51,134.60) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 62.32, 26.00) rectangle (236.93, 44.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 62.32, 32.25) {Distribution:\ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (114.49, 31.00) rectangle (122.49, 39.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{163,207,235}
\definecolor{fillColor}{RGB}{163,207,235}

\path[draw=drawColor,line width= 0.8pt,fill=fillColor] (115.49, 32.00) rectangle (121.49, 38.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (194.42, 31.00) rectangle (202.42, 39.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{186,129,35}

\path[draw=drawColor,line width= 0.8pt] (195.42, 32.00) rectangle (201.42, 38.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (124.49, 32.25) {Post-intervention\ \ \ \ };
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (204.42, 32.25) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 83.80,  6.00) rectangle (215.44, 24.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 83.80, 12.25) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (163.43, 11.00) rectangle (171.43, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.6pt,dash pattern=on 4pt off 4pt ,line join=round] (167.43, 11.00) -- (167.43, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (271.01,195.13);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (173.43, 12.25) {0.25 mg/m\textsuperscript{3}};
\end{scope}
